Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-03 _03_smoothing_tracks.Rmd
prepare edit to fig 5

```{r echo=FALSE}
### plot figures
fig_agg_data <-
  lapply(list_of_agg, function(df) {
    ggplot(df)+
      geom_path(data = data,
                aes(x, y),
                col = "grey20",
                size = 0.2)+
      geom_point(data = data_agg,
                 aes(x, y),
                 size = 0.2,
                 col = pal[3])+
      geom_path(aes(x,y), 
                col = pal[1])+
      geom_point(aes(x,y,
                     group = interval),
                 shape = 19,
                 col = pal[4],
                 size = 2,
                 alpha = 0.6,
                 show.legend = F)+
      ggthemes::theme_few()+
      theme(axis.text = element_blank(),
            axis.title = element_blank(),
            panel.background = element_rect(fill = "white"))+
      coord_cartesian(ylim = c(0.6, NA))
  })
```

@@

```{r echo=FALSE}
# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg)+
  geom_hline(yintercept =
               1 + quantile(data$speed, na.rm = T,
                        probs = c(0.5, 0.95)),
             lty = c(1, 2))+
  geom_errorbar(data = speed_agg_smooth,
                aes(x = factor(interval),
                    ymin = 1 + median - sd,
                    ymax = 1 + median + sd),
                width = 0.2,
                position = position_nudge(x = 0.25)) +
  geom_point(data = speed_agg_smooth,
             aes(x = factor(interval),
                 y = 1 + median),
             shape = 21,
             size = 3,
             fill = pal[3],
             position = position_nudge(x = 0.25)) +
  geom_boxplot(aes(factor(interval), 1 + speed),
               position = position_nudge(x = -0.25,),
               fill = "grey",
               alpha = 0.5,
               show.legend = F, 
               width = 0.25, 
               outlier.size = 0.2)+
  scale_y_log10(label = scales::comma,
                limits = c(NA, 1.005))+
  ggthemes::theme_few()+
  theme(axis.text.y = element_blank())+
  labs(x = "interval (s)",
       y = "speed")
```

```{r echo=FALSE}
# make combined figure
fig_aggregate <-
  wrap_plots(append(fig_agg_data[3:4], list(fig_agg_speed)),
             design = "AABBC")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))

>>>>

```{r echo=FALSE}
### plot figures
fig_agg_data <-
  lapply(list_of_agg, function(df) {
    ggplot(df)+
      # geom_path(data = data,
      #           aes(x, y),
      #           col = "grey20",
      #           size = 0.2)+
      geom_path(data = data_agg,
                 aes(x, y),
                 size = 0.3,
                 col = pal[2])+
      geom_path(aes(x,y), 
                col = pal[4])+
      geom_point(aes(x,y,
                     group = interval),
                 shape = 0,
                 col = pal[4],
                 alpha = 1,
                 show.legend = F)+
      ggthemes::theme_few()+
      theme(axis.text = element_blank(),
            axis.title = element_blank(),
            panel.background = element_rect(fill = "white"))+
      coord_cartesian(ylim = c(0.6, NA))
  })
```

@@

```{r echo=FALSE}
# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg)+
  geom_hline(yintercept =
               1 + quantile(data$speed, na.rm = T,
                        probs = c(0.5, 0.95)),
             lty = c(1, 2))+
  geom_errorbar(data = speed_agg_smooth,
                aes(x = factor(interval),
                    ymin = 1 + median - sd,
                    ymax = 1 + median + sd),
                width = 0.2,
                position = position_nudge(x = 0.25)) +
  geom_point(data = speed_agg_smooth,
             aes(x = factor(interval),
                 y = 1 + median),
             shape = 21,
             size = 3,
             fill = pal[2],
             position = position_nudge(x = 0.25)) +
  geom_boxplot(aes(factor(interval), 1 + speed),
               position = position_nudge(x = -0.25,),
               fill = "grey",
               alpha = 0.5,
               show.legend = F, 
               width = 0.25, 
               outlier.size = 0.2)+
  scale_y_log10(label = scales::comma,
                limits = c(NA, 1.005))+
  ggthemes::theme_few()+
  theme(axis.text.y = element_blank())+
  labs(x = "interval (s)",
       y = "speed")
```

```{r echo=FALSE}
# make combined figure
# fig_aggregate <-
  wrap_plots(append(fig_agg_data[3:4], list(fig_agg_speed)),
             design = "AABBC")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")") &
  theme(plot.tag = element_text(face = "bold"))
